Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-07-11 paper/main.tex
reduced the total number of figures

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{../plot2/Mass/Web.ps}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/VWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/TWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jVWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/jTWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWeb.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vVWebV2.ps}
\includegraphics[width=0.48\textwidth]{../plot2/Mass/vTWebV2.ps}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the peculiar
  velocity of each halo.} 
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
\end{figure*}

@@

\subsection{Mass dependency and other conditions for stronger alignment}

@@

>>>>

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/Web.pdf}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
%\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
%\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
%\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
%\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
%\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
%\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
%\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
%\end{figure*}

@@

\subsection{What drives the alignment}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plot3/Type/256_All.png}
\includegraphics[width=0.48\textwidth]{../plot3/Type/256_Big.png}
\caption{Busy plot. Hard to describe.}
\end{figure*}
